\Title

### 2015-10-13 moho-inversion.tex
Small methods tweaks

In potential field methods,
we must isolate the target anomalous density distribution prior to modeling and
inversion.
In our case, the target is the relief of the real Moho undulating around a
reference Moho.
We do this by removing all other effects from the gravity observations.
The first correction is to remove the
gravity\footnote{The term ``gravity'' refers the sum of the gravitational and
centripetal accelerations.}
of an ellipsoidal Earth (the Normal Earth or reference ellipsoid).
This is done using the closed-form solution presented in \citet{li_ellipsoid_2001}.
The resulting quantity is known as the gravity disturbance,

\begin{equation}
    \delta g(P) = g(P) - \gamma(P)
\end{equation}

@@

\noindent in which $d_i$ is the $i$th element of the $N$-dimensional predicted
data vector $\mbf{d}$, $\mbf{p}$ is the $M$-dimensional parameter vector
containing the Moho depths ($z_k$),
and $f_i$ is the $i$th non-linear function that maps the parameters onto the
data.
\todo{Say something about tesseroid forward modeling and cite paper.}

@@

Both methods require the computationally expensive evaluation of the Jacobian
matrix $\mbf{A}$.
In practice, the derivative in \eq{jacobian} is often calculated through a
first-order finite-difference approximation.
Thus, evaluating $\mbf{A}$ requires $2\times M \times N$ forward modeling
operations for each iteration of the gradient descent algorithm.
When using tesseroids, forward modeling requires several trigonometric function
evaluations as well as adaptive discretization.
\todo{Cite forward modeling paper}
Both factor contribute significantly to the total computation time.

>>>>

In potential field methods,
we must isolate the target anomalous density distribution prior to modeling and
inversion.
In our case, the target is the relief of the real Moho undulating around a
reference Moho.
We do this by removing all other effects from the gravity observations.
The first correction is to remove the
gravity\footnote{The term ``gravity'' refers the sum of the gravitational and
centripetal accelerations.}
of an ellipsoidal Earth (the Normal Earth or reference ellipsoid).
This is done using the closed-form solution presented in
\citet{li_ellipsoid_2001}.
\todo{Needs review}
The resulting quantity is known as the gravity disturbance,

\begin{equation}
    \delta(P) = g(P) - \gamma(P)
\end{equation}

@@

\noindent in which $d_i$ is the $i$th element of the $N$-dimensional predicted
data vector $\mbf{d}$, $\mbf{p}$ is the $M$-dimensional parameter vector
containing the Moho depths ($z_k$),
and $f_i$ is the $i$th non-linear function that maps the parameters onto the
data.
$f_i$ is the radial component of the gravitational attraction of the tesseroid
model.
The gravitational attraction of a tesseroid is calculated using the
Gauss-Legendre Quadrature (GLQ) integration.
The accuracy of the GLQ integration is improved by an adaptive discretization
scheme.
\todo{Cite tesseroids paper.}

@@

Both methods require the computationally expensive evaluation of the Jacobian
matrix $\mbf{A}$.
In practice, the derivative in \eq{jacobian} is often calculated through a
first-order finite-difference approximation.
Thus, evaluating $\mbf{A}$ requires $2\times M \times N$ forward modeling
operations for each iteration of the gradient descent algorithm.
Forward modeling using tesseroids requires several trigonometric function
evaluations and numerical integration.
\todo{Cite forward modeling paper}
Both factors contribute significantly to the total computation time required to
evaluate $\mbf{A}$.
